\chapter{Discussion}
This thesis was partly inspired by the work of Jeon et al., particularly their article attempting to explain the increase in spin pumping below the superconducting transition temperature with a superconducting pure spin current \cite{Jeon2018}. In this article, Jeon et al. have observed an increase in the resonance linewidth $\Delta H$ below the critical temperature for samples with a Nb thickness of 15 nm and 30 nm. Since quasiparticle interactions freeze out at lower temperatures, they argued that the spin current increase can only explained by spin-triplet spincurrents. However, this experiment was only done on a fixed microwave frequency of $f = 20 \ \textrm{GHz}$. This limitation makes it difficult to directly investigate the Gilbert-damping $\alpha$, as $\alpha$ can be best assessed by measuring the slope of the frequency-dependent resonance linewidth (see Eq. (\ref{linewidth equation})). Müller et al. \cite{PhysRevLett.126.087201} and Mangold (unpublished) conducted broadband FMR measurements and found no increase in Gilbert damping below $T_\textrm{C}$, yielding no evidence for spin-triplet supercurrents. Also, samples measured in this thesis also show no increase in $\alpha$ below $T_\textrm{C}$, but rather a decrease, which is consistent with the findings of Müller et al. and Mangold.

A subsequent article by Jeon et al. from 2019 on Permalloy films sandwiched between two Nb layers (100nm) improves upon this and employs methods similar to those used in this thesis, involving frequency-dependent measurements to investigate the Gilbert-damping \cite{Jeon2019}. In the article, the resonance curve is measured for frequencies from 5-20 GHz for temperatures from 2-80 K and the resulting four parameters ($\alpha$, $\Delta H_0$, $M_\textrm{eff}$, $H_\textrm{shift}$) were extracted. In general, the trends observed in their article are mirrored in this thesis, especially when compared to the result for the 45 nm sample.

The researchers observed a similar drop in the Gilbert-damping parameter $\alpha$ from around 0.016 above $T_\textrm{C}$ to 0.0011 at 2 K. This trend closely aligns with the measurements for the 45 nm sample in this thesis (see \ref{fig:45nm_params}), although the absolute values of $\alpha$ are slightly lower in this thesis. The 30 nm sample shows the same trend as well, with a much smaller drop from around 0.01 to around 0.008.

For the resonance offset $\Delta H_0$, a significant increase is visible from around 0 mT near $T_\textrm{C}$ to reaching a maximum at 4 K at slightly above 6 mT and dropping down to 4 mT for 2 K. This increasing trend can be seen on both our samples as well, although at a much smaller scale. The 45 nm sample only has an increase from around 0 mT to 1 mT, while the 30 nm sample has an increase from around 0 mT to 0.04 mT. The absolute values of $\Delta H_0$ are thus significantly smaller in our samples.

The resonance shift $H_\textrm{shift}$ decreases from 0 mT to around -50 mT at 2 K. This trend is also mirrored in the measurements done in this thesis, although the absolute values are again smaller, with the 45 nm sample showing a shift of around -10 mT and the 30 nm sample around -13 mT.

The differences can be attributed to the difference in thickness between the samples used in the article of Jeon et al. and this thesis. A sample with a Nb layer of 100 nm would demonstrate significantly stronger superconducting properties, which would explain the larger change in $\alpha$, $\Delta H_0$ and $H_\textrm{shift}$.

The results of the study done by Jeon et al. \cite{Jeon2019} thus is confirmed by the results obtained in this thesis, especially for the 45 nm sample. 

The spiking behavior near $T_{\textrm{C}}$ for all parameters can potentially be attributed to domains building near $T_{\textrm{C}}$ in the supercondutor, where some domains are superconducting and others are not. An alternative explanation could be that the spike is caused by vortices that are pinned onto defects under $T_\textrm{C}$ suddenly having enough thermal energy to break free and move around. Both explanations lead to a disturbance in the spin-transfer mechanism. This disturbance leads to an incoherent precession of the magnetization, leading to a broadening of the resonance line and a weaker signal. This spike has not been reported yet, and displays interesting 
