\chapter{Conclusion}
This thesis was structured in two parts: 1) The investigation of Gilbert damping and other parameters in HM-SC-FM-SC-HM heterostructures near the critical temperature $T_\textrm{C}$ using FMR, and 2) the development of a fabrication process for a device capable of FMR measurements under a DC-bias current.

Regarding the first part, the results for the sample with $d_\textrm{Nb} = \SI{45}{nm}$ are in good agreement with the literature \cite{Jeon2019} and previous measurements done by Mangold.
The results for the sample with $d_\textrm{Nb} = \SI{30}{nm}$ however shows unexpected behavior for the parameter $M_\textrm{eff}$, which could be attributed to sample aging and degradation. Near the critical temperature, almost all parameters show a spike-like feature, which has not been reported in literature yet. This feature could be attributed to domain formation or vortex motion in the superconductor near $T_\textrm{C}$, disturbing the spin-transfer mechanism.

Regarding the second part, it was verified that cross-linking a resist can be done to create an isolation layer for fabricating a device capable of FMR measurements under a DC-bias. The method of overbaking was identified as a viable method. However, as stated above, Samuel Fülop found a more suitable method using the MLA. This is now the main method used at the chair for creating isolation layers via cross-linking, as it allows for local exposure.
As a next step, fabrication of the same device on asymmetric stacks are planned, to investigate the effect of DC currents and supercurrents on the Gilbert damping.
The microfabrication process was established and a first device was fabricated. However, due to time constraints, no measurements could be performed on this device. Future studies could use this device to investigate the influence of a DC-bias current on the parameters $\alpha$, $\Delta H_0$, $M_\textrm{eff}$ and $H_\textrm{shift}$ in HM-SC-FM-SC-HM heterostructures, potentially allowing further studies of the spikes of the FMR parameters near $T_\textrm{C}$.